---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# omicsdatapaper

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

This golem is an installable version of the Omics data paper R shiny app: https://mdmtrv.shinyapps.io/Omics_data_paper/

The Omics Data Paper Generator app, packaged within this golem, emulates the functionality of the automatic workflow for streamlined import of ENA metadata into manuscript integrated inside Pensoft's ARPHA Writing Tool. You can read more about it in this [abstract](https://biss.pensoft.net/article/59041/) and [blogpost](https://blog.pensoft.net/2020/06/16/streamlined-import-of-omics-metadata-from-the-european-nucleotide-archive-ena-into-an-omics-data-paper-manuscript/).

## Requirements
You need R and R Studio to run this app. We've tested it with the following versions of R and RStudio:

- R 3.0.1+
- RStudio Desktop 1.3.1093

## Installation

You can install the latest version of omicsdatapaper from [github](https://github.com/) with:

``` r
devtools::install_github("mdmtrv/omicsdatapaper")
```

## Use

The omicsdatapaper golem has only one function: to run the Omics Data Paper Generator app locally on your machine. This is how to do it:

```{r example}
library(omicsdatapaper)
run_app()
```

That's all!
The package handles all dependencies and imports the required [jats-skeleton.xml](https://github.com/pensoft/omics-data-paper-shinyapp/blob/master/jats-skeleton.xml).
